Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-07-15 man/ecosystems/ms_ecosystems.Rmd
update text and figures

---
title: "Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies along a climatic gradient in the rear-edge"
author: "A.J. Perez-Luque^1,2^; G. Gea-Izquierdo^3^ and Zamora, R.^1,2^"
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: ../../templates/template_ms.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecosystems.csl
---

@@

## **Short Title**: Resilience of relict oaks in the rear-edge (máximo 45 caracteres)

@@

## **Author Contributions**
AJPL, GGI and RZ conceived of or desing the study. AJPL, GGI and RZ conducted field work and collected the data. AJPL and GGI conducted lab work and led article preparation. AJPL analyzed data and wrote the paper. GGI and RZ contributed in the writing process. All authors contribute to the drafts and gave final approval for publication.

# Abstract
* Global change challenges forest ecosystems particularly in species-specific dry locations where land-use legacies have modified the forest structure as result of intensive human-pressures in the past. We analyzed forest resilience of adult trees to drought and climate change of relict Mediterranean *Quercus pyrenaica* Willd. populations in the Southern Iberian Peninsula. Forest resilience was analyzed using both dendroecological growth estimates and greenness (NDVI) as proxies for secondary and primary growth respectively. Additionally forest history were inferred from an exhaustive review of historical documents.

@@

## keywords
extreme drought, resilience, rear-edge, *Quercus pyrenaica*, tree-growth, dendrocronology, remote-sensing

>>>>

---
title: "Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies along a climatic gradient in the rear-edge"
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 6
    highlight: null
    reference_docx: ../../templates/template_ms.docx
bibliography: ../../refs/references.bib
csl: ../../refs/ecosystems.csl
---

@@

## **Short Title**
Resilience of relict oaks in the rear-edge (max. 45 characters)

## Authors [^+^] 
A.J. Perez-Luque^1,2,a^; G. Gea-Izquierdo^3,b^ and Zamora, R.^1,2,c^

@@

^a^ ajperez@ugr.es

^b^ gea.guillermo@inia.es

^c^ rzamora@ugr.es

[^+^]: Author Contributions. AJPL, GGI and RZ conceived of or design the study. AJPL, GGI and RZ conducted field work and collected the data. AJPL and GGI conducted lab work and led article preparation. AJPL analyzed data and wrote the paper. GGI and RZ contributed in the writing process. All authors contribute to the drafts and gave final approval for publication.

## Abstract
* Global change challenges forest ecosystems particularly in species-specific dry locations where land-use legacies have modified the forest structure as result of intensive human-pressures in the past. We analyzed forest resilience of adult trees to drought and climate change of relict Mediterranean *Quercus pyrenaica* Willd. populations in the Southern Iberian Peninsula. Forest resilience was analyzed using both dendroecological growth estimates and greenness (NDVI) as proxies for secondary and primary growth respectively. Additionally forest history were inferred from an exhaustive review of historical documents.

@@

## Keywords
extreme drought, resilience, rear-edge, *Quercus pyrenaica*, tree-growth, dendrocronology, remote-sensing

### 2019-07-15 man/figures/0_figures.Rmd
update figures std anomalies and EVI profile
update figures
update figures and chronos
update text and figures

@@

>>>>

```{r, include=FALSE}
options(knitr.duplicate.label = 'allow')
```

@@

```{r child = 'browning.Rmd'}
```

```{r child = 'bai_cronos.Rmd'}
```

```{r child = 'growth_changes.Rmd'}
```

**Figure 6.** Resilience metrics of the tree-growth for severe drought events since 1950. *Left*: Resistance (*Rt*); *Center*: Recovery (*Rc*); *Right*: Resilience (*Rs*). Points indicate resilience metrics for oak populations: SJ (*blue*), CA-High (*red*) and CA-Low (*green*). Resilience metrics were computed for each population (sample depth > 10) and drought event. Gray line represents overall relationship for each Resilience metrics.

![](../../man/figures/svg/fig_6_95.jpg){height=750px}

```{r child = 'resilience_metrics.Rmd'}
```

```{r child = 'ring_climate.Rmd'}
```

```{r child = 'cumulative_prec.Rmd'}
```

```{r child = 'plot_spei12.Rmd'}
```

```{r child = 'residual_chronos.Rmd'}
```

```{r child = 'gc_perc_trees.Rmd'}
```

```{r child = 'corr_plot_years.Rmd'}
```

```{r child = 'correla_boot_sites.Rmd'}
```

```{r child = 'evi_vs_severe_droughts.Rmd'}
```

**Figure S8.** Resilience metrics of the tree-growth for severe drought events since 1950 (excluding 1995 drought event). *Left*: Resistance (*Rt*); *Center*: Recovery (*Rc*); *Right*: Resilience (*Rs*). Points indicate resilience metrics for oak populations: SJ (*blue*), CA-High (*red*) and CA-Low (*green*). Resilience metrics were computed for each population (sample depth > 10) and drought event. Gray line represents overall relationship for each Resilience metrics.

![](../../man/figures/svg/fig_6_no95.jpg){height=750px}
